gij bent 2

### 2024-11-26 paper/paper.qmd
Further clean up regression table

```{r #tbl-other-coefficients}
# All other coefficients start with an underscore
other_coefficients <- coefficients_full[coefficients_full$feature %>% substr(1,1) == "_",]
# Change "removed" to "retained"
other_coefficients$retained = ifelse(other_coefficients$coefficient == 0, "no", "yes")
# Friendly names
other_coefficients$feature <- gsub("_(.+)", "\\1", other_coefficients$feature)
other_coefficients$feature <- gsub("(dialect_)", "dialect: ", other_coefficients$feature)
other_coefficients$feature <- gsub("(is_)", " ", other_coefficients$feature)
other_coefficients$predictor <- other_coefficients$feature
other_coefficients$coefficient <- other_coefficients$coefficient %>% formatd(3)
# Only keep interesting columns
other_coefficients <- other_coefficients[, names(other_coefficients) %in% c("coefficient", "predictor", "retained")]
# Re-order
other_coefficients <- other_coefficients[,c(3, 1, 2)]
# Sort
other_coefficients$coefficient <- as.numeric(other_coefficients$coefficient)
other_coefficients <- other_coefficients[order(other_coefficients$coefficient,
                                               decreasing=TRUE),]
# Remove row indices
rownames(other_coefficients) <- NULL
# Output to document
other_coefficients
```

>>>>

```{r #tbl-other-coefficients}
# All other coefficients start with an underscore
other_coefficients <- coefficients_full[coefficients_full$feature %>% substr(1,1) == "_",]
# Change "removed" to "retained"
other_coefficients$retained = ifelse(other_coefficients$coefficient == 0, "no", "yes")
# Friendly names
other_coefficients$feature <- gsub("_(.+)", "\\1", other_coefficients$feature)
other_coefficients$feature <- gsub("(dialect_)", "dialect: ", other_coefficients$feature)
other_coefficients$feature <- gsub("(gender_)", "gender: ", other_coefficients$feature)
other_coefficients$feature <- gsub("(reply_)", "reply: ", other_coefficients$feature)
other_coefficients$feature <- gsub("(is_)", " ", other_coefficients$feature)
other_coefficients$predictor <- other_coefficients$feature
other_coefficients$coefficient <- other_coefficients$coefficient %>% formatd(3)
# Only keep interesting columns
other_coefficients <- other_coefficients[, names(other_coefficients) %in% c("coefficient", "predictor", "retained")]
# Re-order
other_coefficients <- other_coefficients[,c(3, 1, 2)]
# Sort
other_coefficients$coefficient <- as.numeric(other_coefficients$coefficient)
other_coefficients <- other_coefficients[order(other_coefficients$coefficient,
                                               decreasing=TRUE),]
# Remove row indices
rownames(other_coefficients) <- NULL
# Output to document
other_coefficients
```
